---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(GGally)
library(tidytext)
library(wordcloud2) 
library(topicmodels)
```

| Field     | Question                                                                        |
|:-----------------------------------|:-----------------------------------|
| timestamp | Timestamp                                                                       |
| q1        | How many hours did you sleep last night?                                        |
| q2        | How many hours did you work (e.g. do homework, or a job) after you left school? |
| **q3**    | How many hours did you spend relaxing after you left school?\*\*                |
| q4        | What did you do to relax last night?                                            |
| q5        | How do you feel today?                                                          |
| q6        | Which best describes you (your answer should be the same every day)             |

## Start by labelling your data

-   Labeling help you understand your data
-   Folks often overestimate how long it takes
-   If outsourcing...
    -   Start by labeling the data yourself
    -   Have an odd number of people labeling
    -   Come up with consistent rules (heuristics)

```{r}
# Use set_names to name columns
survey_df <- read_csv("survey_results.csv") %>%
  set_names(c(
    "timestamp",
    "q1",
    "q2",
    "q3",
    "q4",
    "q5",
    "q6",
    "watch_shows_movies",
    "sleep",
    "chat",
    "food",
    "friends",
    "video_games",
    "listen_music",
    "book"
  ))
survey_df
```

```{r}
survey_df %>% select(timestamp)
```

## Plot Bar Chart of Common Tags

```{r}
# Select label columns
# Use colSums to get sum of each column
# Use stack to get "long" format of column sums
survey_df %>%
  select(
    "watch_shows_movies",
    "sleep",
    "chat",
    "food",
    "friends",
    "video_games",
    "listen_music",
    "book"
  ) %>%
  colSums() %>%
  stack() %>%
  ggplot() +
    geom_bar(aes(y = ind, x = values), stat = "identity")

```

## Plot Correlation Between Tags

```{r}
# Use select and ggcorr to plot correlations
survey_df %>%
  select(
    "watch_shows_movies",
    "sleep",
    "chat",
    "food",
    "friends",
    "video_games",
    "listen_music",
    "book"
  ) %>%
  ggcorr()

```

## Plot Word Counts

Each **document** is a response, and each **token** is a word.

```{r}
# select the q4 column
# unnest_tokens separates each documents into tokens
# count() the occurrences of each token
# set the width and height while ggsave

survey_df %>%
  select(q4) %>%
  unnest_tokens(word, q4) %>%
  count(word) %>%
  ggplot() +
    geom_bar(aes(y = reorder(word, n), x = n), stat = "identity")

ggsave(
  "word_counts.png",
  width = 5,
  height = 10
)


```

## Word Clouds (and why they not as good)

<https://r-graph-gallery.com/196-the-wordcloud2-library.html> Warning: <https://www.data-to-viz.com/graph/wordcloud.html>

```{r}
survey_df %>%
  select(q4) %>%
  unnest_tokens(word, q4) %>%
  count(word) %>%
  wordcloud2()
```

## Topic Modelling

<https://www.tidytextmining.com/topicmodeling.html>

```{r}
survey_lda <- survey_df %>%
  select(q4) %>%
  mutate(document = 1:n()) %>%
  unnest_tokens(word, q4) %>%
  group_by(document) %>%
  add_count(word) %>%
  cast_dtm(term = word, document = document, value = n) %>%
  LDA(k = 2, control = list(seed = 1234))

survey_topics <- tidy(survey_lda, matrix = "beta")
survey_topics
```

```{r}
survey_top_terms <- survey_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

survey_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```

```{r}
beta_wide <- survey_topics %>%
  mutate(topic = paste0("topic", topic)) %>%
  pivot_wider(names_from = topic, values_from = beta) %>% 
  filter(topic1 > .001 | topic2 > .001) %>%
  mutate(log_ratio = log2(topic2 / topic1))

beta_wide %>%
  ggplot() +
  geom_bar(aes(y = reorder(term, log_ratio), x = log_ratio), stat = "identity")

ggsave(
  filename = "two_topic_model.png",
  width = 5,
  height = 10
)
```

-   How do you determine right number of topics?
-   How do you determine what the topics are?
